SDG contributions

### 2023-09-11 article/article.qmd
some steps on merging country

mag_2021_paper_author_affil <- spark_read_csv(
  sc, 
  "/tklebel/mag-2021-03-15/PaperAuthorAffiliations.txt",
  name = "mag2021_paper_author_affil", delimiter = "\\t",
  memory = FALSE, header = FALSE)

@@

>>>>

affil_cols <- c("paperid", "authorid", "affiliationid", "authorsequencenumber",
                "originalauthor", "originalaffiliation")

mag_2021_paper_author_affil <- spark_read_csv(
  sc, 
  "/tklebel/mag-2021-03-15/PaperAuthorAffiliations.txt",
  name = "mag2021_paper_author_affil", delimiter = "\\t",
  memory = FALSE, header = FALSE, columns = affil_cols)

@@

```{r}
# check if we got countries for most affils in the full set
merged <- mag_2021_paper_author_affil %>% 
  distinct(affiliationid) %>% 
  left_join(affils) %>% 
  collect()

merged_orig_data <- author_paper_affiliations %>% 
  distinct(affiliationid) %>% 
  left_join(affils) %>% 
  collect()
```
